Hydras \& Co.

### 2022-03-17 doc/part-hydras.tex
corrections chapter 4 (up to page 86)

\subsubsection{A sigma-type for \texorpdfstring{$\epsilon_0$}{epsilon0}}

@@

\emph{From Module~w}

@@

First, we declare a notation scope for \texttt{E0}.

\input{movies/snippets/E0/E0Scope}

Then we redefine the predicates of comparison.

\label{Predicates:Lt-E0}

\input{movies/snippets/E0/LtLeDef}

@@

\begin{exercise}[\gaia]
  Look for the \gaia-theorem which corresponds to \texttt{succb\_iff}.
\end{exercise}

>>>>

\subsubsection{\texttt{E0}: a sigma-type for \texorpdfstring{$\epsilon_0$}{epsilon0}}

@@

\emph{From Module~\href{../theories/html/hydras.Epsilon0.E0.html\#E0}{Epsilon0.E0}}

@@

First, we declare a notation scope for \texttt{E0}, then we redefine the predicates of comparison.

\input{movies/snippets/E0/E0Scope}
\label{Predicates:Lt-E0}
\input{movies/snippets/E0/LtLeDef}

@@

\begin{exercise}[\gaiasign]
  Look for the \gaia-theorem which corresponds to \texttt{succb\_iff}.
\end{exercise}
